We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-04-11 paper/paper.tex
reply

In Illustris-1-Dark we use the center of mass position of the 27 pairs
in Illustris-1 to find the matching halo pairs.
After discarding the pairs with less than 15 detected subhalos in one
of the halos we end up with a total of 24 pairs in Illustris-1-Dark. 
This corresponds to a pair number density of $\sim 2 \times10^{-5}$
pairs Mpc$^{-3}$. 
Appendix A shows the physical  properties (stellar masses, maximum
circular velocities, radial velocities and separation) of those
pairs.

@@

Appendix A compares the physical properties (stellar masses, maximum
circular velocities, radial velocities and separation) in those
pairs against the results from the Illustris-1 simulations.

>>>>

In Illustris-1-Dark we use the center of mass position of the 27 pairs
in Illustris-1 to find the matching halo pairs.
After discarding the pairs with less than 15 detected subhalos in one
of the halos we end up with a total of 24 pairs in Illustris-1-Dark. 
This corresponds to a pair number density of $\sim 2 \times10^{-5}$
pairs Mpc$^{-3}$. 
Appendix A shows the maximum, circular velocities, radial velocities and separation of those pairs.

@@

Appendix A compares the physical properties (maximum circular
velocities, radial velocities and separation) in those pairs against
the results from the Illustris-1 simulations.
